The population of long-period exoplanets I. --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive

### 2016-03-17 document/ms.tex
a few words

@@

Since the simulated parameters in the injection and recovery tests described
above were sampled from the prior distribution $p(\params_{\{R,\,P\}})$, the
easiest way to estimate \eq{full-comp} is to take the ratio of the weighted
histogram of the recovered injections to the weighted histogram of all
simulations where each simulation is weighted by
$Q_{\mathrm{win},k} (\params) \, Q_{\mathrm{geom},k} (\params)$ evaluated at
the parameters of the simulation.

@@

Geometric:

Temporal:

\begin{eqnarray}
Q_{\mathrm{temp},k} (\params) &=& \frac{T_k}{P}
\end{eqnarray}
where $T_k$ is the total observing baseline for target $k$.
Combined with the detection efficiency $Q_{\mathrm{det}}(\params)$ (assumed to
be constant for each target), the total completeness as a function of the
parameters is
\begin{eqnarray}
Q_k(\params) &=& Q_{\mathrm{det},k}(\params) \,
                 Q_{\mathrm{temp},k} (\params) \,
                 Q_{\mathrm{geom},k} (\params) \\
&=& Q_{\mathrm{det},k}(\params) \,
    \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,
    R_{\star,k}\,T_k
    \, \left[\frac{1 + e(\params)\,\sin \omega(\params)}{1-e(\params)^2}\right]
    \, P^{-5/3} \quad.
\end{eqnarray}

The likelihood function for the catalog of planet candidates is
\begin{eqnarray}
p(\{\params_n\}\,|\,\poppars) &\propto&
    \exp \left(
        \int f_\poppars (\params)\,\sum_{k=1}^K Q_k(\params) \dd\params
    \right) \, \prod_{n=1}^N f_\poppars (\params_n) \quad.
\end{eqnarray}

Therefore
\begin{eqnarray}
\int f_\poppars (\params)\,\sum_{k=1}^K Q_k(\params) \dd\ln P\dd\ln R &=&
    \bar{Q}\,\int Q_{\mathrm{det}}(\params)\,f_\poppars(\params)\,P^{-5/3}
        \dd\ln P\dd\ln R
\end{eqnarray}
where
\begin{eqnarray}
\bar{Q} &=& \sum_{k=1}^K
    \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}\,T_k
\quad.
\end{eqnarray}

The easiest way to evaluate this integral in practice is to use Monte Carlo
integration to find
\begin{eqnarray}
\int Q_{\mathrm{det}}(\params)\,f_\poppars(\params)\,P^{-5/3}\dd\ln P\dd\ln R
&=& \frac{F}{J}\sum_{j=1}^J Q_{\mathrm{det}}(P^{(j)},\,R^{(j)})\,
        f_\poppars(P^{(j)},\,R^{(j)})
\end{eqnarray}
where
\begin{eqnarray}
F &=& \frac{3}{5}\,[P_\mathrm{min}^{-5/3}-P_\mathrm{max}^{-5/3}]\,
      [\ln R_\mathrm{max} - \ln R_\mathrm{min}]
\end{eqnarray}
and
\begin{eqnarray}
P^{(j)} \sim P^{-8/3} &\mathrm{and}&
\ln R^{(j)} \sim \mathcal{U}(\ln R_\mathrm{min},\,\ln R_\mathrm{max})
\end{eqnarray}

\begin{eqnarray}
f_\poppars (\params) &=& \frac{1}{f_0}\,C\,P^\alpha\,R^\beta
\end{eqnarray}
where
\begin{eqnarray}
f_0 &=&
    \int_{P_\mathrm{min}}^{P_\mathrm{max}}
    \int_{R_\mathrm{min}}^{R_\mathrm{max}}
    P^\alpha\,R^\beta\dd\ln P\dd\ln R
\end{eqnarray}

>>>>

\newcommand{\rate}{{\ensuremath{\Gamma}}}

@@

Since the simulated parameters in the injection and recovery tests described
above were sampled from the prior distribution $p(\params_{\{R,\,P\}})$, the
easiest way to estimate \eq{full-comp} is to take the ratio of the weighted
histogram of the recovered injections to the weighted histogram of all
simulations where each simulation is weighted by
$Q_{\mathrm{win},k} (\params) \, Q_{\mathrm{geom},k} (\params)$ evaluated at
the parameters of the simulation.
\dfmtodo{Some figure} shows the measured completeness (\eq{full-comp}) as a
function of planet radius and orbital period.

\dfmtodo{Analytic fit?}

@@

Using the catalog of exoplanet discoveries (\dfmtodo{some section}) and the
measurement of the search completeness (\dfmtodo{some section}), we can now
estimate the occurrence rate of long-period exoplanets.
This inference can be simplified by making a few strong assumptions that are
only weakly justified.
First, we make the strong assumption that none of the candidates are
astrophysical false positives (background eclipsing binaries, the secondary
eclipse of a long-period binary system, \etc).
We revisit this assumption and discuss its validity in \dfmtodo{some section}.
Next, we model the occurrence of exoplanets as a Poisson process
(\dfmtodo{CITE}) with a rate function $\rate_{\poppars} (R,\,P)$ parameterized
by some parameters \poppars.
This assumption leads to the commonly used likelihood function
(\dfmtodo{CITE})
\begin{eqnarray}
\ln p (\{w_j\}_{j=1}^J\,|\,\poppars) =
    \sum_{j=1}^J \ln \rate_{\poppars} (R_j,\,P_j)
    - \int \rate_{\poppars} (R,\,P)\,Q(R,\,P)\dd R\dd P
    + \mathrm{constant} \quad.
\end{eqnarray}
Since our catalog of discoveries is small, we will only make limited
inferences about the population.
For the purposes of this paper, we will simply estimate the period of
long-period planets ($2\,\mathrm{yr} \le P < 15\,\mathrm{yr}$) in two radius
bins $0.1\,R_\mathrm{J} \le R < 0.5\,R_\mathrm{J}$ and $0.5\,R_\mathrm{J} \le
R < R_\mathrm{J}$.
